Bird beak's elaboration and innovation

### 2025-04-14 Analysis/03-Elaboration_innovation_analysis.Rmd
Update 03-Elaboration_innovation_analysis.Rmd

write.csv(elaborations_global, file = "../Data/Processed/elaborations_distributions.csv")
write.csv(innovations_global, file = "../Data/Processed/elaborations_distributions.csv")

>>>>

write.csv(elaborations_global, file = "../Data/Processed/elaborations_distributions.csv")
write.csv(innovations_global, file = "../Data/Processed/innovations_distributions.csv")
